---
title: "Modelling lipid physiology and energy imbalance during weight loss."
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Mathematical model

This document introduces a mathematical model for the lipid physiology and energy imbalance during a great weight loss. It consists in a system of ODE :
$$\frac{dFM}{dt} = \frac{1-p}{\rho_F}(EI-EE)$$
$$\frac{dLM}{dt} = \frac{p}{\rho_L}(EI-EE)$$ 
where FM is the fat mass, LM the lean mass, EI the energy intake and EE the energy expenditure. And $$p=\frac{C}{C+F}$$

```{r import, echo=FALSE}
rm(list=ls())
library(deSolve)
library(coda)
library(rootSolve)
library(FME)

dat <- read.table(file = "CLINICAL(copietravail).csv", sep= ',', header = TRUE)
  ######################################
  # BODYWEIGHT, FAT MASS AND LEAN MASS #
  ######################################
BW0 <- dat$BW0
BW1 <- dat$BW1
BW2 <- dat$BW2
BW5 <- dat$BW5

FM0 <- dat$TBFD0
FM2 <- dat$TBFD2
FM5 <- dat$TBFD5

adjust = subset(FM0/dat$TBFB0, is.na(FM0/dat$TBFB0)==F)
mean_adjust = mean(adjust)

FM0[18]=mean_adjust*dat$TBFB0[18]

#On a BW = LM + FM

LM0 <- BW0-FM0
LM2 <- BW2-FM2
LM5 <- BW5-FM5

  ##################
  # AGE AND HEIGHT #
  ##################
age0 <- dat$Age0
age2 <- dat$Age2
age5 <- dat$Age5
H <- dat$Height

BMI0 <- dat$BMI0
BMI1 <- dat$BMI1
BMI2 <- dat$BMI2
BMI5 <- dat$BMI5

adjust2 = subset(BMI1-BMI2, is.na(BMI1)==F)
mean_adjust2 = mean(adjust2)
BMI1[9] <- BMI2[9] - mean_adjust2
BMI1[20] <- BMI2[20] - mean_adjust2
BMI1[21] <- BMI2[21] - mean_adjust2

  ########
  # TIME #
  ########
T0 <- rep(0,41)
T2 <- dat$T2
T1 <- T2/2
T5 <- dat$T5

  ##############
  # PARAMETERS #
  ##############
pf <- 39500 #kJ/kg
pl <- 7600 #kJ/kg
gf <- 13 #kJ/kg/day
gl <- 92 #kJ/kg/day
nf <- 750 #kJ/kg 
nl <- 960 #kJ/kg
Btef <- 0.1
Bat <- 0.14
C <- 10.4*pl/pf #kg
tau <- 14 #jours
  #####################
  # PHYSICAL ACTIVITY #
  #####################
d0 <- ((1-Btef)*1.5-1)*(10*BW0+625*H-5*age0-161)*4.184
d2 <- ((1-Btef)*1.5-1)*(10*BW2+625*H-5*age2-161)*4.184
d5 <- ((1-Btef)*1.5-1)*(10*BW5+625*H-5*age5-161)*4.184

  #######################
  # ENERGY PARTITIONING #
  #######################
p2 <- C/(C+FM2) 
p5 <- C/(C+FM5)


```

## Modelling the weight loss of patients

There are some parameters which need to be determined from the data given by the Karolinska Institute : the energy expenditure (EE), the energy intake (EI) and K a constant. Kevin D. Hall gives us a formula to estimate the energy expenditure :
$$EE = K + \gamma_FF + \gamma_LL + \delta + TEF+AT+\eta_F\frac{dF}{dt}+\eta_L\frac{dL}{dt}$$
$$EE = \frac{K + \gamma_FF + \gamma_LL + \delta + TEF+AT+EI(\eta_F\frac{1-p}{\rho_F}+\eta_L\frac{p}{\rho_L})}{1+\eta_F\frac{1-p}{\rho_F}+\eta_L\frac{p}{\rho_L}}$$
TEF is the factor introducing the thermic effect of feeding and AT is the adaptive thermogenesis. Both represent the response of a sudden change of energy intake:
$TEF =  \beta_{TEF}\Delta EI$ and $AT = \beta_{TEF}\Delta EI(1-e^{-\frac{t}{\tau}})$
When the patient is weight stable it means that $EI = EE$. For example before the surgery the patients maintain their weight as $EI_0 = EE_0$.
It means that 
$$EE_0 = K + \gamma_FF_0 + \gamma_LL_0 + \delta_0$$
We can estimate $EE_0$ thanks to the Mifflin equation for women:
$$EE_0 = EI_0 = 10BW_0 + 625H - 5age_0 -161$$
Thus the constant K can be determined.
```{r energy, echo=FALSE}
  #########################
  # INITIAL ENERGY INTAKE #
  #########################
EI0 <- (10*BW0 + 625*H -5*age0-161)*1.5*4.184
EIsurg <- c()
EIfinal <- c()

EI <- function(t, EI0, EIsurg, EIfinal)
{
  if (t<=0){
    EI0
  }
  else if (t<=500){
    EIsurg
  }
  else{
    EIfinal
  }
}

  ##############################
  # INITIAL ENERGY EXPENDITURE #
  ##############################
EE0 <- EI0
EE <- function(t,EIi, EIs, EIf, k, h, a, FM, LM){
  B <- Btef+Bat*(1-exp(-t/tau))
  PA <- ((1-Btef)*1.5-1)*4.184*(10*(FM+LM)+625*h-5*(a+t/365)-161)
  partF <- FM/(C+FM)
  partL <- 1-partF
  result <- (k + gf*FM + gl*LM + PA - EIi*B + EI(t, EIi, EIs, EIf)*(B + partF*nf/pf + partL*nl/pl))/(1 + partF*nf/pf + partL*nl/pl)
  result
}

  ##############
  # K CONSTANT #
  ##############
K <- EI0 - gf*FM0 - gl*LM0 - d0



```

```{r equation, echo=FALSE}
  ##############
  # EDO SYSTEM #
  ##############

EqBW <- function(t, y, parameters){
  
  EIi <- parameters[1]
  k <- parameters[2]
  h <- parameters[3]
  a <- parameters[4]
  EIs <- parameters[5]
  EIf <- parameters[6]
  partF <- y[1]/(C+y[1])
  partL <- 1-partF
  
  dF <- partF/pf * (EI(t, EIi, EIs, EIf) - EE(t,EIi, EIs, EIf, k, h, a, y[1], y[2]))
  dL <- partL/pl * (EI(t, EIi, EIs, EIf) - EE(t,EIi, EIs, EIf, k, h, a, y[1], y[2]))
  list(c(dF, dL))
}

```

```{r individual graph, echo=FALSE}
  ########################
  # SOLVE FOR PATIENT 40 #
  ########################
soltime <- seq(0,2200)
parameters <- c(EI0[40], K[40], H[40], age0[40])
init <- c(fatmass = FM0[40],leanmass = LM0[40])
Data <- data.frame(time = c(T2[40],T5[40]), fatmass = c(FM2[40],FM5[40]) , leanmass= c(LM2[40],LM5[40]))

modelcost <- function(P) {
  sol <- lsoda(y=init, times=soltime, func = EqBW, parms = c(parameters,P[1],P[2]))
  return(modCost(sol,Data))
}

Fit <- modFit(f = modelcost, p = c(7800,10000))

EIsurg <- Fit$par[1]
EIfinal <- Fit$par[2]
  
parameters <- c(EI0[40], K[40], H[40], age0[40], EIsurg, EIfinal)
init <- c(fatmass = FM0[40],leanmass = LM0[40])
bestfit <- lsoda(y=init, times=soltime, func = EqBW, parms = c(parameters))

  #####################
  # ENERGY RATE GRAPH #
  #####################

graphtime <- seq(-100,2200)
graphEI= rep(EI0[40], 100)
graphEE = rep(EE0[40], 100)
for (i in 101:2301){
  graphEI[i] <- EI(graphtime[i], EI0[40], EIsurg, EIfinal)
  graphEE[i] <- EE(graphtime[i], EI0[40], EIsurg, EIfinal, K[40], H[40], age0[40], bestfit[i-100,2], bestfit[i-100,3])
}

plot(graphtime, graphEI, type="l", xlab="Days", ylab="Energy rate ", col=1, ylim=c(1000, 15000))
lines(graphtime, graphEE, type ="l", lty = 1, col=2)
legend("bottomright",lty=c(1,1), cex=0.7, col=c(1,2), legend=c("Energy Intake rate", "Energy Expenditure rate"))
title(main= "Energy rates time course")


  ############################
  # WEIGHT TIME COURSE GRAPH #
  ############################

graphFM <- c(rep(FM0[40], 100), bestfit[,2])
graphLM <- c(rep(LM0[40], 100), bestfit[,3])
graphBW <- c(rep(BW0[40], 100), bestfit[,2]+bestfit[,3])

plot(graphtime, graphFM, type="l", ylim=c(0,160), xlab="Days", ylab="Weight in kg")
lines(graphtime, graphBW, type = "l", lty =1, col=4)
lines(graphtime, graphLM, type = "l", lty =1, col="dodgerblue4")
points(T0[40], FM0[40], pch=3)
points(T2[40], FM2[40], pch=3)
points(T5[40], FM5[40], pch=3)
points(T0[40], BW0[40], pch=19, col=4)
points(T2[40], BW2[40], pch=19, col=4)
points(T5[40], BW5[40], pch=19, col=4)
points(T0[40], LM0[40], pch=3, col="dodgerblue4")
points(T2[40], LM2[40], pch=3, col="dodgerblue4")
points(T5[40], LM5[40], pch=3, col="dodgerblue4")
title(main= "Bodyweight time course")
legend("bottomright", lty=c(1,1,1), legend=c("Bodyweight", "Fatmass","Leanmass"), col=c(4,1,"dodgerblue4"), cex=0.7)

```
```{r comparison, echo=FALSE}
dat2 <- read.table(file = "planner.csv", sep= ',', header = TRUE)
ptime <- dat2$Day
pBW <- dat2$Weight
pFM <- dat2$FM
pLM <- pBW - pFM
pEI <- dat2$Intake
pEE <- dat2$Expenditure
pEIsurg <- pEI[1]
pEIfinal <- pEI[length(pEI)]

soltime <- seq(0,2200)
parameters <- c(EI0[40], K[40], H[40], age0[40], pEIsurg, pEIfinal)
init <- c(fatmass = FM0[40],leanmass = LM0[40])
bestfit <- lsoda(y=init, times=soltime, func = EqBW, parms = c(parameters))

graphEI <- c()
graphEE <- c()
for (i in 1:2201){
  graphEI[i] <- EI(soltime[i], EI0[40], pEIsurg, pEIfinal)
  graphEE[i] <- EE(soltime[i], EI0[40], pEIsurg, pEIfinal, K[40], H[40], age0[40], bestfit[i,2], bestfit[i,3])
}

plot(soltime, graphEI, type="l", xlab="Days", ylab="Energy rate ", col=1, xlim=c(0, 500), ylim=c(1000, 15000))
lines(ptime, pEI, lty =2)
lines(soltime, graphEE, type ="l", lty = 1, col=2)
lines(ptime, pEE, type ="l", lty = 2, col=2)
legend("bottomright",lty=c(1,1,2,2), cex=0.7, col=c(1,2,1,2), legend=c("Energy Intake rate", "Energy Expenditure rate", "Planner EI", "Planner EE"))

graphFM <- bestfit[,2]
graphLM <- bestfit[,3]
graphBW <- bestfit[,2]+bestfit[,3]

plot(soltime, graphFM, type="l", xlim=c(0, 500), ylim=c(0,140), xlab="Days", ylab="Weight in kg")
lines(ptime, pFM, type = "l", lty =2)
lines(soltime, graphBW, type = "l", lty =1, col=4)
lines(ptime, pBW, type = "l", lty =2, col=4)
lines(soltime, graphLM, type = "l", lty =1, col="dodgerblue4")
lines(ptime, pLM, type = "l", lty =2, col="dodgerblue4")
legend("bottomright", lty=c(1,1,1,2,2,2), legend=c("BW", "FM","LM", "Planner BW", "Planner FM", "Planner LM"), col=c(4,1,"dodgerblue4",4,1,"dodgerblue4"), cex=0.7)

```