---
title: "Modelling lipid physiology and energy imbalance during weight loss."
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Mathematical model

This document introduces a mathematical model for the lipid physiology and energy imbalance during a great weight loss. It consists in a system of ODE :
$$\frac{dFM}{dt} = \frac{1-p}{\rho_F}(EI-EE)$$
$$\frac{dLM}{dt} = \frac{p}{\rho_L}(EI-EE)$$
where FM is the fat mass, LM the lean mass, EI the energy intake and EE the energy expenditure. 
```{r import, echo=FALSE}
rm(list=ls())
library(deSolve)

dat <- read.table(file = "CLINICAL(copietravail).csv", sep= ',', header = TRUE)
```

## Modelling with R

There are some parameters wich need to be determined from the data given by the Karolinska Institute : the energy expenditure (EE), the energy intake (EI), the difference of energy intake (dEI) and K a constant.

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
